Fast and scalable Gaussian process modeling with applications to astronomical time series \vspace{-3\baselineskip}

### 2017-03-02 paper/ms.tex
a few additions to the docs

{\item For $Q = 1/\sqrt{2}$, \eq{sho-psd} simplifies to
\begin{eqnarray}\eqlabel{granulation-psd}
S(\omega) = \sqrt{\frac{2}{\pi}}\,\frac{S_0}{(\omega/\omega_0)^4+1} \quad.
\end{eqnarray}
A model like this has been used to model the granulation is Solar data
\citep{Michel:2009}}, which has a kernel of
\begin{equation}
k(\tau) = S_0\,\omega_0\,e^{-\frac{1}{\sqrt{2}}\,\omega_0\,\tau}\,
    \cos{\left(\frac{\omega_0\,\tau}{\sqrt{2}}-\frac{\pi}{4}\right)}.
\end{equation}

>>>>

{\item For $Q = 1/\sqrt{2}$, \eq{sho-psd} simplifies to
\begin{eqnarray}\eqlabel{granulation-psd}
S(\omega) = \sqrt{\frac{2}{\pi}}\,\frac{S_0}{(\omega/\omega_0)^4+1} \quad.
\end{eqnarray}
This, in turn, is the most commonly used model for the background granulation
noise in asteoreseismic \citep{Kallinger:2014} and helioseismic
\citep{Harvey:1985, Michel:2009} analyses.
The Fourier transform of this PSD corresponds to the kernel
\begin{equation}
k(\tau) = S_0\,\omega_0\,e^{-\frac{1}{\sqrt{2}}\,\omega_0\,\tau}\,
    \cos{\left(\frac{\omega_0\,\tau}{\sqrt{2}}-\frac{\pi}{4}\right)}.
\end{equation}}
